---
title: "Lab 2 ATMS 748"
author: "Jack Tarricone"
date: "2/21/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2) 
library(dplyr) 
library(lubridate) 
library(chron)
library(openair)
```
# Directions
•Acquire data with your program on data card\
•Copy data table to your PC in CSV format (Loggernet: <Data><CardConvert>)\
•Copy your CSV data to UNR Box\
•Copy other lab teams’ CSV data files from Box\
•Write a program to read the data and make time series plots\
•Turn in plot of timeseries of your  HMP-155 temperature measurements and ensemble-averaged temperature measurements with standard deviation (error bars or patch)\
•Turn in plot of timeseries of your HMP-155 relative humidity measurements and ensemble-averaged relative humidity measurements with standard deviation (error bars or patch)\
•Turn in windrose plot of your wind measurements (wind speed and direction)
•Turn in electronic copy of program\


# Data Formatting
```{r}
# read in csvs created in last script
g1 <-read.csv("/Users/jacktarricone/atms_748/data-code/lab2_data/csvs/lab2_g1.csv")
g2 <-read.csv("/Users/jacktarricone/atms_748/data-code/lab2_data/csvs/lab2_g2.csv")
g4 <-read.csv("/Users/jacktarricone/atms_748/data-code/lab2_data/csvs/lab2_g4.csv")
g5 <-read.csv("/Users/jacktarricone/atms_748/data-code/lab2_data/csvs/lab2_g5.csv")
```

```{r}
# transform date_time back into a R date
g1$date_time <-ymd_hms(g1$date_time)
g2$date_time <-ymd_hms(g2$date_time)
g4$date_time <-ymd_hms(g4$date_time)
g5$date_time <-ymd_hms(g5$date_time)
```

```{r}
# trim each df down so it has the same date_time range, cutting off the back data in the start
g1_filt <-filter(g1, date_time >= ymd_hms("2022-01-25 17:45:00") 
                 & date_time <= ymd_hms("2022-02-01 15:45:00"))
g2_filt <-filter(g2, date_time >= ymd_hms("2022-01-25 17:45:00") 
                 & date_time <= ymd_hms("2022-02-01 15:45:00"))
g4_filt <-filter(g4, date_time >= ymd_hms("2022-01-25 17:45:00") 
                 & date_time <=ymd_hms("2022-02-01 15:45:00"))
g5_filt <-filter(g5, date_time >= ymd_hms("2022-01-25 17:45:00") 
                 & date_time <=ymd_hms("2022-02-01 15:45:00"))
```

# 1. RH
```{r}
## create new df with RH for all 4 groups
# bind all the groups RH values together
rh_df <-cbind(g1_filt$RH, g2_filt$RH, g4_filt$RH, g5_filt$RH) 
rh_df <-as.data.frame(rh_df) # convert to df
date_time <-ymd_hms(g1_filt$date_time) # convert date again
rh <-cbind(date_time, rh_df) # bind date col
colnames(rh) <-c("date_time","g1_RH", "g2_RH","g4_RH","g5_RH")

# create mean col for plot
rh$mean <-(rh$g1_RH+rh$g2_RH+rh$g4_RH+rh$g5_RH)/4

# create sd col for plot
rh$sd <-sd(rh$mean)

```

```{r}
# plot
theme_set(theme_classic(12)) # set theme for plotting
ggplot(rh) +
  geom_line(aes(x = date_time, y = mean), col = "black") +
  geom_ribbon(aes(x = date_time, ymin = mean-sd, ymax = mean+sd, fill = "+/- One Standard Deviation"), alpha=.2)+
  scale_fill_manual("",values="grey12") +
  labs(title = "HMP RH Ensemble Average Jan 25th - Feb 1st 2022") +
  ylab("RH (%)") +
  xlab("Date") +
    theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position = c(.85,.9),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 9, face = "bold"),
        legend.margin = margin(t=0, unit='cm'),
        legend.key = element_rect(size = .2))
```
**Figure 1.** This plot displays the ensemble average relative humidity (RH) with plus and minus one standard deviation for Groups 1, 2, 4, and 5 between January 25th and February 2nd, 2022. Group 3 was omitted because the data contained significant errors and was not logged correctly. Group 1 & 2 also had errors in their data, with the RH values only unrealistically varying between 35-45%

# 2. Air Temperature 

```{r}
# create new df with air temp for all 4 groups
# bind all the groups AT values together
at_df <-cbind(g1_filt$AirTC_Avg, g2_filt$AirTC_Avg, g4_filt$AirTC_Avg, g5_filt$AirTC_Avg)
at_df <-as.data.frame(at_df) # convert to df
date_time <-ymd_hms(g1_filt$date_time) # convert date
at <-cbind(date_time, at_df) # bind date and data
colnames(at) <-c("date_time","g1_at", "g2_at","g4_at","g5_at")

# create mean col
at$mean <-(at$g1_at+at$g2_at+at$g4_at+at$g5_at)/4

# create sd col
at$sd <-sd(at$mean)
```

```{r}
# plot
ggplot(at) +
  geom_line(aes(x = date_time, y = mean), col = "red") +
  geom_ribbon(aes(x = date_time, ymin = mean-sd, ymax = mean+sd, fill = "+/- One Standard Deviation"), alpha=.2)+
  scale_fill_manual("",values="grey12") +
  labs(title = "HMP Air Temperature Ensemble Average Jan 25th - Feb 1st 2022") +
  ylab("Temperature (C)") +
  xlab("Date") +
    theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position = c(.8,.1),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 9, face = "bold"),
        legend.margin = margin(t=0, unit='cm'),
        legend.key = element_rect(size = .2))
```
**Figure 2.** This plot displays the ensemble average HMP air temperature with plus and minus one standard deviation for Groups 1, 2, 4, and 5 between January 25th and February 2nd, 2022. Similar to RH, Group 3's HMP data was omitted because it was not logged correctly. The variance temperature data was consistent when compared to the RH data.


# 3. Wind Rose
```{r}
# read in group 3 sonic data csv
g3 <-read.csv("/Users/jacktarricone/atms_748/data-code/lab2_data/csvs/jack_eric.csv")
```

```{r}
# format date
g3$date <-ymd_hms(g3$date_time)

## correct offset of -2
g3$windDirection <- g3$windDirection -2
id <- which(g3$windDirection < 0)
g3$windDirection[id] <- g3$windDirection[id] + 360
```

```{r fig.height = 6, fig.width = 6, fig.align = "center"}
# plot using windRose function from openair package
windRose(g3, ws = "windSpeed", wd = "windDirection", angle = 10, ws.int = .5, angle.scale = 45,
         cols = c("yellow", "blue", "green", "black"), width = 1.5, auto.text = FALSE, paddle = FALSE) 
```
**Figure 3.** This wind rose plot shows direction, speed, and frequency of wind events from a 2-D sonic anemometer from February 1st - 8th, 2022 in Reno, NV. The majority of wind speeds were below 1 m/s, while the most common wind directions were from the southeast and northwest.