---
title: "Lab 3b ATMS 748"
author: "Jack Tarricone"
date: "4/15/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2);theme_set(theme_classic(12)) 
library(dplyr) 
library(lubridate) 
library(chron)
library(openair)
```

# Directions
Lab 3b requirements (due April 19)\
a. Results section with paragraph description of data (time span, data quality)\

d. Timeseries plot of upwelling and downwelling shortwave radiation with legend.
Comment on the plot.\

e. Timeseries plot of upwelling and downwelling longwave radiation with legend.
Comment on the plot.\
f. Timeseries plot of net radiation. Comment on the plot.\
g. Timeseries plot of albedo. Comment on the plot.\
h. Discussion section with 2 paragraphs of data analysis on topics of your choice using
the data collected.\


# Load Data
Data formatting done in seperate script ```tarricone_lab3_data_qaqc.R", which is attached.
```{r}
# read in csvs created in last script
# read data back in and format date_time back to a date
tiger_data <-read.csv("/Users/jacktarricone/atms_748/atms748_lab3/tiger_data.csv")
tiger_data$date_time <-ymd_hms(tiger_data$date_time)

# transform date_time back into a R date
tiger_data$date <-as.Date(tiger_data$date)
```


### b. Plot of windrose for your wind data. Comment on it.\
```{r}
## correct offset of -2
tiger_data$windDirection <- tiger_data$windDirection -4
id <- which(tiger_data$windDirection < 0)
tiger_data$windDirection[id] <- tiger_data$windDirection[id] + 360
```

```{r fig.height = 6, fig.width = 6, fig.align = "center"}
# plot using windRose function from openair package
windRose(tiger_data, ws = "windSpeed", wd = "windDirection", 
         angle = 10, ws.int = 1.5, angle.scale = 45,
         cols = c("yellow", "blue", "green", "black"), 
         width = 1.5, auto.text = FALSE, paddle = FALSE) 


# trim each df down so it has the same date_time range, cutting off the back data in the start
# g1_filt <-filter(g1, date_time >= ymd_hms("2022-01-25 17:45:00") 
#                  & date_time <= ymd_hms("2022-02-01 15:45:00"))

```
### c. Timeseries plot of temperature for 5TM (if you have it), 107, HMP-155, panel
temperature, sonic temperature all on the same plot (with legend)

```{r}
# plot
ggplot(tiger_data) +
  geom_line(aes(x = date_time, y = AirTemp, col = "Atmos-22")) + # panel temp
  geom_line(aes(x = date_time, y = T107_C_Avg, col = "CS-107")) + #107 ground temp
  geom_line(aes(x = date_time, y = AirTC_Avg, col = "HMP-155")) + # hmp air temp
  geom_line(aes(x = date_time, y = PTemp_C, col = "CR100X Panel Temp.")) + # panel temp
  ylim(c(-10,30))+
  scale_colour_manual(name = "Sensor",
                      values=c("goldenrod","black","firebrick","forestgreen")) +
  labs(title = "Comparing Different Temperature Sensors 4/1 - 4/6/2022") +
  ylab("Temperature (C)") +
  xlab("Date") +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position = c(.85,.23),
        legend.text = element_text(size = 7),
        legend.title = element_text(size = 8, face = "bold"),
        legend.margin = margin(t=0, unit='cm'),
        legend.key = element_rect(size = .1))
```
**Figure 2.** This plot displays temperature measurements for the CS-107, HMP-155, and the CR1000X data logger panel temperature between April 1st and April 6th, 2022. The CS-107 was buried a few centimeters into the top of the soil, while HMP-155, ATMOS-22, panel temperatures are logger changes in air temperature.

## d. Timeseries plot of upwelling and downwelling shortwave radiation with legend
```{r}
# plot
ggplot(tiger_data) +
  geom_line(aes(x = date_time, y = SWin_Avg, col = "SWin")) + 
  geom_line(aes(x = date_time, y = SWout_Avg, col = "SWout")) + 
  scale_colour_manual(name = "Energy Flux", 
                      values=c("slateblue","tomato")) +
  labs(title = "Incoming and Outgoing SW Radiation 4/1 - 4/6/2022") +
  ylab("Shortwave Radiation (W/m^2)") +
  xlab("Date") +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position = c(.85,.95),
        legend.text = element_text(size = 7),
        legend.title = element_text(size = 8, face = "bold"),
        legend.margin = margin(t=0, unit='cm'),
        legend.key = element_rect(size = .1))
```
**Figure 3.** Comparison between incoming and outgoing SW radiation at the Tiger met station. Incoming SW is substantially higher than out going, which makes sense from the low albedo bare soil below the radiometer. Variability in the data is caused by cloud cover absorbing incoming radiation, with April 2nd being a completely cloud free day.


## e. Timeseries plot of upwelling and downwelling longwave radiation with legend

```{r}
# plot
ggplot(tiger_data) +
  geom_line(aes(x = date_time, y = LWin_Avg, col = "LWin")) + # panel temp
  geom_line(aes(x = date_time, y = LWout_Avg, col = "LWout")) + #107 ground temp
  scale_colour_manual(name = "Energy Flux",
                      values=c("cornsilk4","maroon4")) +
  labs(title = "Incoming and Outgoing LW Radiation 4/1 - 4/6/2022") +
  ylab("Lonwave Radiation (W/m^2)") +
  xlab("Date") +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position = c(.85,.95),
        legend.text = element_text(size = 7),
        legend.title = element_text(size = 8, face = "bold"),
        legend.margin = margin(t=0, unit='cm'),
        legend.key = element_rect(size = .1))
```
**Figure 4.** Comparison between incoming and outgoing LW radiation at the Tiger met station. ***MORE***

## f. Timeseries plot of net radiation
```{r}
# calculate net radiation
tiger_data$net_rad <-tiger_data$SWnet_Avg+tiger_data$LWnet_Avg

# plot
ggplot(tiger_data) +
  geom_line(aes(x = date_time, y = net_rad), col = "darkorchid4") + 
  labs(title = "Net Radiation 4/1 - 4/6/2022") +
  ylab("Net Radiation (W/m^2)") +
  xlab("Date")
```
**Figure 5.** Comparison between incoming and outgoing LW radiation at the Tiger met station. ***MORE***

## Timeseries plot of albedo.
```{r}
# calculate net radiation
tiger_data$albedo <-(tiger_data$SWout_Avg)/tiger_data$SWin_Avg
tiger_data$time <-hms(tiger_data$time)

# filter out low values which are a night when there is no solar
filt <-filter(tiger_data, albedo > .25)

# plot
ggplot(filt) +
  geom_line(aes(x = date_time, y = albedo)) + # panel temp
  ylim(c(0,1))+
  labs(title = "Albedo 4/1 - 4/6/2022") +
  ylab("Albedo") +
  xlab("Date") 

```
**Figure 6.**  ***MORE***


## h. Discussion section with 2 paragraphs of data analysis on topics of your choice using
the data collected.

